Delivering Reliable Software in the European Scientific Arena: Evolution of Methodologies and New Trend Analysis

### 2017-12-21 paper-ieee-trans.tex
added changes

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/DavideSalomoni}}]{Davide Salomoni}
Davide SAlomoni is Director of Technology at the Italian National Institute for Nuclear Physics (INFN). He has 27 years of international experience in private and public environments related to distributed computing and communication technologies. He currently leads the Software Development and Distributed Systems department at CNAF, the INFN National Center Dedicated to research and development on IT technologies, located in Bologna, Italy. He was Project Coordinator of INDIGO-DataCloud funded by the EC Horizon2020 that developed innovative open source computing and storage solutions.
\end{IEEEbiography}

>>>>

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/DavideSalomoni}}]{Davide Salomoni}
Davide SAlomoni is Director of Technology at the Italian National Institute for Nuclear Physics (INFN). He has 27 years of international experience in private and public environments related to distributed computing and communication technologies. He currently leads the Software Development and Distributed Systems department at CNAF, the INFN National Center Dedicated to research and development on IT technologies, located in Bologna, Italy. He was Project Coordinator of INDIGO-DataCloud, a project funded by the EC Horizon2020, that developed innovative open source computing and storage solutions.
\end{IEEEbiography}
